% !TeX program=lualatex

%Requires lualatex or xelatex and installed fontss
\documentclass[aspectratio=169,t]{beamer}
\usetheme[
	%Here you can add package options for the theme
	numbering=fraction,% fraction/counter/none
]{cccamp19}





\usepackage{layout}

%local definitions, generally not necessary
\newcommand*{\code}[1]{\texttt{#1}}
\begin{document}
	

%Linebreaks set with \\ also incrase the base indent	
\title{CCCamp19-beamer}
\subtitle{\LaTeX{} beamer for CCCamp19}
\author{marei \email{chaos@texhackse.de}}

\maketitle
	
\begin{frame}{Fonts}
	This bundle requires Marvel and Fira Sans fonts installed.
	
	Fira is part of \TeX{} Live and Mik\TeX{}. Marvel can be downloaded from GitHub \url{https://github.com/google/fonts/tree/master/ofl/marvel}
	
	The normal Text Font ist Fira Sans. Code Font is Fira Code, with Ligatures enabled (shown on next slide).
		
	Examples for Marvel:
	\headerfont marvel regular\\
	\textit{marvel italic}\\
	\bfseries marvel bold\\
	\itshape marvel bold italic
\end{frame}

	
\begin{frame}[fragile]{The Code Font Supports some Ligatures}
	Turn them off using package option: \code{codeligatures=off}
	
	This option can only be set globally.
	\begin{verbatim} 
	=>
	==
	!=	 
	<--
	<->
	www	
	\end{verbatim}
\end{frame}

\begin{frame}[fragile]{Package Options}
	You can either use the coloring options as package option or locally. To change it inside the Document use
	
	\begin{verbatim}
	\ChangeOptions{rocket=communication}
	\end{verbatim}
	The available options are:
	\begin{description}
	\item[rocket] choose rocket(s) for progressbar
	\item[frametitle] color the frametitle or switch back to changing
	\item[titleimage] replace the fullpage-image for the title slide
	\item[titlepos] Coordinate of north west corner of the title \& subtitle box
	\end{description}
\end{frame}

\begin{frame}{frametitle}
In default setting the color are chaging from slide to slide. 
To choose a specific color set frametitle to one of the values:

chaos, communication, camp, all
\end{frame}

\begin{frame}{rocket}
The rocket option acts similar to the frametitle one. 

Beside the values chaos, communication, camp and all, there is also a none-option to turn off all rockets.
\end{frame}

\begin{frame}[plain]{A plain frame}
this is another possibility to locally turn off the rockets
\end{frame}


%Example for Changing the Layout.
\ChangeOptions{rocket=chaos,frametitle=chaos}


\begin{frame}{Design Credits}
The Design for this template is based on the official Camp Design by Sven Sedivy.

It can be found on \url{https://events.ccc.de/2019/07/09/design-release-chaos-communication-camp-2019/}
\end{frame}

\begin{frame}
	tbc
\end{frame}

\end{document}